### 2012-05-31 web/12.su.reg/exams/exam4.su.12.tex
Exam 4

\vfill
\centerline{\Large CS 2510 Exam 2 -- Summer 2012}

@@

%% -----------------------------------------------------------------------------
%% 
\pts{30}
\begin{problem}

Binary trees are one of the most widely used data structures in
computer science.  Here are three examples of binary trees of numbers:

\begin{verbatim}
         5        1           3
                   \         / \
                    2       4  18
                              /  \
                             9    12
                            /    /
                           7    3
\end{verbatim}

Nodes in a binary tree carry data, which in this case are numbers, and
a node has a left and right subtree.  Binary trees, like lists, may
contain \emph{any} number of elements, including 5, 8, 19, and 0.

\begin{enumerate}
\item Design a data definition for binary trees.  It must adequately
  represent any possible binary tree.

\item Give class diagrams corresponding to the data definition from
  part A.

\item Design a {\tt mirror} method that computes the mirror image of a
  binary tree.  For example, the mirror image of the above trees would
  be:

\begin{verbatim}
     5        1           3
             /           / \
            2           18  4
                       /  \
                     12    9
                       \    \
                        3    7
\end{verbatim}
\end{enumerate}

\end{problem}
\newpage
\ 
\end{document}

>>>>

\vfill
\centerline{\Large CS 2510 Exam 4 -- Summer 2012}

@@

%% -----------------------------------------------------------------------------
%% 
\pts{45}
\begin{problem}
An association list is a way of representing an association between
values.  For example, you might you use an association list to
associate students with their grades, or battleships with their
position, or bank account numbers with their account balances.

The representation of an association list is much like a typical list,
except that every ``cons'' has \emph{two} elements and the rest of the
list.  One element is a ``key'', the other is its association.

Here is a data definition for association lists parameterized over the
types of keys and their values:

\begin{verbatim}
interface Assoc<K,V> {}

class EmptyAssoc<K,V> implements Assoc<K,V> {}

class ConsAssoc<K,V> implements Assoc<K,V> {
  K key;
  V val;
  Assoc<K,V> rest;
  ConsAssoc(K key, V val, Assoc<K,V> rest) {
    this.key = key;
    this.val = val;
    this.rest = rest;
  }
}
\end{verbatim}

\begin{enumerate}
\item Develop the visitor pattern for association lists.
\item Design an implementation of an association list visitor that
  looks up the (first) value associated to a given key.  If the key is
  not in the list, the visitor shoud throw an exception.
\item Using the double dispatch approach, design a {\tt same} method
  that determines if this association list is structurally equal to a
  given association list.
\end{enumerate}
\end{problem}
\newpage
\ 
\newpage
\ 
\end{document}
